% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jiajun "Thomas" Liang}

\basicInfo{
  \email{toml@usc.edu} \textperiodcentered\ 
  \phone{(213)-713-7499} \textperiodcentered\ 
  \linkedin[Thomas Liang]{https://www.linkedin.com/in/thomas-liang-52270823b/} \textperiodcentered\
  \github[ThmsLiang]{https://github.com/ThmsLiang}}

\section{Education}
\datedsubsection{\textbf{University of Southern California}, Los Angeles, California}{Aug 2020 -- May 2024 (expected)}
\textit{B.S} in Computer Science (CSCI), Dean's List, 3.5/4.0

\section{Experience}
\datedsubsection{\textbf{iFLYTEK Co.}, Hefei, China}{Jun 2023 - Aug 2023}
\role{Software Developer Intern - Backend | Node.js, Express.js, MongoDB}{}
  iFLYTEK is China's leading company in AI solutions and consumer products.
\begin{itemize}
  \item My Role: Helped build a new after-sale service backend for both consumers and stores.
  \begin{itemize}
    \item Built with \textbf{Express.js} framework and used \textbf{Mongoose} library to produce REST API for CRUD.
    \item Stored and queried GeoJSON data to find nearest stores, utilized 20\% speed with geospartial indexes.
    \item Integrated \textbf{Socket.IO} to project to enhance real-time communications between users and stores.
  \end{itemize}
  \item Helped support after-sale services for products sold by millions and expected above \textbf{10,000 DAU}.
\end{itemize}

\datedsubsection{\textbf{RecApp for USC}, Los Angeles, CA}{Jan 2022 - May 2022}
\role{Software Developer Intern| Java, Firebase, Android, JUnit}{}
  A student team to design an \textbf{android app} to manage appointments for campus recreational centers.
\begin{itemize}
  \item Worked with two other students and used \textbf{Git} for code collaboration (top 1 contributor).
  \item My Role: Designed schemas, built main activity + database interface following \textbf{repository pattern}.
  \begin{itemize}
    \item Coded in Java in \textbf{Android Studio} and used \textbf{Firebase} for NoSQL database and sign-in authentication. 
    \item Wrote \textbf{JUnit} for whitebox testing and used \textbf{UIAutomator} for blackbox testing in Google Map API.
    \item Followed \textbf{Agile Scrum Methodology} and went through a sprint phase for new functionalities.
  \end{itemize}
  \item Tried by more than 30 students and received above 80\% positive comments on user experience.
\end{itemize}

\section{Projects}
\datedsubsection{\textbf{Distributed Cache System}}{\emph{Go, HTTP, Protobuf}}
  A LRU \textbf{HTTP-based distributed cache system} written by \textbf{Golang}. (Visible on my Github page)
\begin{itemize}
  \item Built HTTP server and client for peers to communicate. Used \textbf{consistent hashing} for load balance.
  \item Allowed \textbf{concurrent read/write} with Mutex and implemented \textbf{singleflight} to avoid cache breakdown.
  \item Transferred \textbf{Protobuf} data to optimize communications between peers and improve extensibility.
\end{itemize}

\datedsubsection{\textbf{AWS-Deployed Full Stack Website Development}}{\emph{HTML/CSS, Vanilla.js, PHP, MySQL}}
  Developed a 9-page website allowing users to create watchlists and search movies through OMDB API.
\begin{itemize}
  \item Used \textbf{MySQLi} library in PHP for CRUD in \textbf{MySQL}, normalized data to reduce redundancy.
  \item Organized layout with \textbf{BootStrap} grid system and Parsed API with \textbf{jQuery AJAX} in frontend.
  \item Deployed with \textbf{AWS} by buildling an Apache server in an EC2 instance and using RDS for database.
\end{itemize}

\datedsubsection{\textbf{Multithreaded Traffic Throttling Web Server}}{\emph{C++11, Socket Programming}}
  A simple \textbf{web server} that can read HTTP requests and send responses with desired files through socket.
\begin{itemize}
  \item Implemented with Multithreading using \textbf{C++11} so it can handle multiple connections at a time.
  \item Achieved \textbf{traffic throttling} by outputting byte streams with limited rate for throughput stability.
\end{itemize}

\section{Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C/C++, Java, Python, PHP, Javascript, HTML/CSS, SQL, Bash/Shell, Go
  \item Tech Stack: MySQL, Firebase, Android, React.js, Docker, Django, SQLite, Node.js, MongoDB, AWS
\end{itemize}



\end{document}
